%begining of latex
\documentclass[9pt]{extarticle}
\input{packages.tex}
\input{configs.tex}
\begin{document}
\pagenumbering{gobble}
\noindent
\begin{tikzpicture}
	\path (0,0) coordinate (left) -- (\linewidth,0) coordinate (right);
	\node [anchor = north west, inner sep = 0pt,scale = 1.6] (name) at (left) {%
		\bfseries\Large
		Muhammad Hashim};
        \node [anchor = north west, inner sep = 0pt, scale = 1.3] (title) at ([yshift = -1ex]name.south west){%
            \bfseries
            Electrical Engineer};
        \node [anchor = north west, inner sep = 1ex] (info0) at ([yshift = -1ex] title.south west) {
            \varBox{\linewidth}{\begin{itemize}[nosep,align=left,labelwidth=\widthof{W:},leftmargin = !,font=\bfseries]
            \item[\faMapMarker*] Mit Ghamr - Dakahliyya
                \begin{multicols*}{2}
                \item[\faMobile*] 01008424732  - 01559544732             
                \item[\faWhatsapp] 01008424732             
                \item[\faTelegram] 01008424732             
                \columnbreak 
                \item[\faAt] m.hashim.666666@gmail.com 
                \item[\faLinkedin] linkedin.com/in/muhammad-hashim-04ab56197/ 
                \item[\faGithub] https://github.com/CommradeGeneral 
            \end{multicols*}
            \end{itemize}}};
        \begin{scope}[on background layer]
            \fill [light!40] (info0.north west) rectangle (right |- current bounding box.south);
        \end{scope}
\end{tikzpicture}

\columnratio{0.6}
\begin{paracol}{2}
\section{Summary}

Electrical Engineer with over 3 years of experience in elevator systems maintenance,
commissioning, and control panel design for elevator systems. Proficient in troubleshooting electrical faults for various elevator systems, PLC programming,
and motor drive systems. Seeking to contribute technical expertise and continuous improvement mindset in a
dynamic engineering environment.

\section{Work experience}

\begin{expbox}[title = {\bfseries Maintenance Engineer}]
	 {\bfseries Egypt Gulf for Elevators and Escalators (EGGEEC)} 
	 \begin{itemize}[nosep,align = left, leftmargin = !, labelwidth = \widthof{L:}] 
		 \item[\faCalendar*] 1/12/2023 - Present
		 \item[{\faMapMarker*}] Heliopolis Chemical Industries (Military Factory 81), Cairo - Bilbeis Desert Road, Obour City \par(Location: 30.1949N, 31.4244E)
	 \end{itemize}
{	\color{light}\dotfill}\smallskip 
	 \begin{itemize}[nosep,align = left, leftmargin = !, labelwidth = \widthof{L:}]\raggedright
\item Conduct scheduled and preventive maintenance for various elevator systems.
                            \item Replace damaged or expired components to ensure operational safety.
                            \item Inspect, troubleshoot, and resolve mechanical and electrical faults.
                            \item Supervise a team of technicians and ensure work quality and safety compliance.
                            \item Review electrical schematics and document maintenance activities.	 \end{itemize}
\end{expbox}
\begin{expbox}[title = {\bfseries Testing \& Commissioning Engineer}]
	 {\bfseries Egypt Gulf for Elevators and Escalators (EGGEEC)} 
	 \begin{itemize}[nosep,align = left, leftmargin = !, labelwidth = \widthof{L:}] 
		 \item[\faCalendar*] 1/9/2021 - 30/11/2023
		 \item[{\faMapMarker*}] Heliopolis Chemical Industries (Military Factory 81), Cairo - Bilbeis Desert Road, Obour City \par(Location: 30.1949N, 31.4244E)
		 \item[{\seg\char"EA8D}] New Administrative capital (R6)
	 \end{itemize}
{	\color{light}\dotfill}\smallskip 
	 \begin{itemize}[nosep,align = left, leftmargin = !, labelwidth = \widthof{L:}]\raggedright
   \item Supported installation and commissioning of elevator systems for 4000+ units of same Fuji product.
                            \item Provided technical assistance and troubleshooting during installation.
                            \item Ensured installations followed design guidelines and industry standards.
                            \item Reviewed user manuals and circuit diagrams for installation accuracy.
                        	 \end{itemize}
\end{expbox}
\begin{expbox}[title = {\bfseries Junior Maintenance Engineer}]
	 {\bfseries Ash-Sherif for melamine} 
	 \begin{itemize}[nosep,align = left, leftmargin = !, labelwidth = \widthof{L:}] 
		 \item[\faCalendar*] 20/1/2021 - 30/7/2021
		 \item[{\faMapMarker*}] Al-Khanka
	 \end{itemize}
\end{expbox}

\section{Education}

\begin{expbox}[title = {\bfseries Bachelor's Degree in Electrical Engineering}]
	\begin{itemize}[nosep,align = left, leftmargin = !, labelwidth = \widthof{L:}]\raggedright
		\item[\faUniversity] Faculty of Engineering - Mansoura University.
		\item[\faCalendar*] 2013 - 2019
	\end{itemize}
\end{expbox}


\switchcolumn  
\section{Languages}

\languageitem[5]{Arabic}{Native}\par\medskip
\languageitem[3.1]{English}{B1}

\section{Skills}


\begin{description}[nosep, align = left, style=nextline]\raggedright
	\item[Elevator Commissioning \& Troubleshooting]
	{\color{light}Including different elevator control systems}
	\par
	\inlineitemi[4]{Local elevator systems troubleshooting}
	\inlineitemi[4]{Fuji elevators commissioning and troubleshooting}
	\inlineitemi[4]{Motor Drives}
	\inlineitemi[5]{Relaying Control}
	\inlineitemi[3]{Basic Electronics}
	\item[Industrial Automation]
	\inlineitemi[5]{Relaying Control}
	\inlineitemi[4]{PLC Siemens S7 series}
	\inlineitemi[3]{PLC Delta DVP series}
	\inlineitemi[4]{Motor Drives}
	\inlineitemi[3]{Industrial Communication}
	\inlineitemi[3]{SCADA WinCC}
	\inlineitemi[1]{HMI Siemens}
	\item[Embedded Systems]
	\inlineitemi[3.5]{8-bit Microcontrollers (PIC - AVR)}
	\inlineitemi[2]{STM32 Families}
	\item[Software Tools]
	\inlineitemi[4.3]{TIA portal}
	\inlineitemi[4.4]{SIMATIC Manager}
	\inlineitemi[2.5]{WinCC}
	\inlineitemi[4]{Inkscape}
	\inlineitemi[1.9]{AUTOCAD}
	\inlineitemi[4]{Word}
	\inlineitemi[3]{Excel}
	\inlineitemi[3]{Power Point}
	\item[Programming Languages]
	\inlineitemi[4.5]{PLC Step7 languages (LAD \& STL \& SCL)}
	\inlineitemi[4]{C/C++}
	\inlineitemi[2.3]{ARM32 Assembly}
	\inlineitemi[2.5]{Python}

\end{description}

\section{Courses \& Achievements}

\begin{expbox}[title = {\bfseries\raggedright Industrial Automation (PLC advanced)}]
	 {\bfseries\raggedright HA Consulting Center} 
	\begin{itemize}[nosep,align = left, leftmargin = !, labelwidth = \widthof{L:}]\raggedright
		\item[\faCalendar*] 5/4/2025 - Ongoing
		\item[\faMapMarker*] Al-Abbasiyya/Cairo. 
		\item[{\bfseries Tracks:}] \phantom{.}
		\begin{itemize}[nosep,leftmargin = *, align = left] \raggedright
			\item PLC Advanced
			\item Industrial Communication
			\item SCADA/HMI
		\end{itemize}
	\end{itemize}
	\end{expbox}
\begin{expbox}[title = {\bfseries\raggedright Industrial Automation (Classic control + PLC Basic Diploma)}]
	 {\bfseries\raggedright HA Consulting Center} 
	\begin{itemize}[nosep,align = left, leftmargin = !, labelwidth = \widthof{L:}]\raggedright
		\item[\faCalendar*] 21/5/2021 - 15/8/2021
		\item[\faMapMarker*] Al-Abbasiyya/Cairo. 
		\item[{\bfseries Tracks:}] \phantom{.}
		\begin{itemize}[nosep,leftmargin = *, align = left] \raggedright
			\item Classic Control
			\item PLC (basic)
			\item VVVF Motor Drives
		\end{itemize}
	\end{itemize}
	\end{expbox}

\section{Personal Info}

\begin{itemize}[nosep,align = left, leftmargin = !, labelwidth = \widthof{L:}]\raggedright

            \item[\faMapMarker*] Mit Ghamr - Dakahliyya
            \item[\faBirthdayCake] 22/8/1994\end{itemize}

\end{paracol}
\end{document}
